Differentially Private Bayesian Inference

### 2018-03-29 main.tex
fix problem in laplace dilation property

\subsection{Dilation Property of Laplace Noise}
\label{sec_Dila}
\begin{lem}
For 1-dimensional Laplace distribution, $h(z) = \frac{1}{2} e^{-|z|}$, $\alpha = \frac{\epsilon}{2}$, $\beta = \frac{\epsilon}{2 \rho_{\delta/3}(|z|)}$ or $ \frac{\epsilon}{2 ln(2/\delta)}$. We have some prior knowledge that $|\lambda| \leq \beta$, the $h$ has dilation property:
\begin{equation*}
Pr[z \in S] \leq e^{\frac{\epsilon}{2}} Pr[z \in e^{\lambda} S] + \frac{\delta}{2}
\end{equation*}
\end{lem}

@@

\begin{itemize}
	\item \textbf{case 1: $\lambda > 0$}

	\begin{equation*}
	\begin{split}
	\because\ 		& 	h(e^{\lambda} z) =  \frac{1}{2} e^{-|e^{\lambda} z|} < \frac{1}{2} e^{-|z|} = h(z)\\
	\therefore\		& 	\frac{Pr[z \in e^{\lambda} S]}{Pr[z \in S]} 
						= \frac
						{\int_{e^{\lambda} S}{} \frac{1}{2}e^{-|z|} dz}
						{\int_{S}{} \frac{1}{2}e^{-|z|} dz} 
						= \frac
						{\int_{S}{} \frac{1}{2}e^{-|e^{\lambda}z|} e^{\lambda} dz}
						{\int_{S}{} \frac{1}{2}e^{-|z|}dz} \\
					&	= \frac{e^{-|e^{\lambda}z|} e^{\lambda}}{e^{-|z|}}
						= \frac{e^{\lambda} h(e^{\lambda} z)}{h(z)}
						\leq e^{\lambda}\\
	\therefore\		&	ln(\frac{e^{\lambda} h(e^{\lambda} z)}{h(z)})
						\leq \lambda \\
	\because\		&	\lambda \leq \beta = \frac{\epsilon}{2 ln(3 / \delta)}, \delta < 1 \\
	\therefore\		&	\lambda \leq \frac{\epsilon}{2} \\
	\therefore\		&	\frac{Pr[z \in e^{\lambda} S]}{Pr[z \in S]} \leq \frac{\epsilon}{2} \\
	\end{split}
	\end{equation*}

>>>>

\subsection{Dilation Property of Laplace Noise}
\label{sec_Dila}
\begin{lem}
For 1-dimensional Laplace distribution: $h(z) = \frac{1}{2} e^{-|z|}$, $\alpha = \frac{\epsilon}{2}$, $\beta = \frac{\epsilon}{2 \rho_{\delta/3}(|z|)}$ or $ \frac{\epsilon}{2 ln(2/\delta)}$ and $|\lambda| \leq \beta$, the dilation property holds for any $z$ sampled from $h$:
\begin{equation*}
Pr[z \in S] \leq e^{\frac{\epsilon}{2}} Pr[z \in e^{\lambda} S] + \frac{\delta}{2}
\end{equation*}
\end{lem}

@@

\begin{itemize}

	From the integral substitution property, we have:

	\begin{equation*}
	\begin{split}
	\frac{Pr[z \in e^{\lambda} S]}{Pr[z \in S]} 
						= &\frac
						{\int_{e^{\lambda} S}{} \frac{1}{2}e^{-|z|} dz}
						{\int_{S}{} \frac{1}{2}e^{-|z|} dz} 
						= \frac
						{\int_{S}{} \frac{1}{2}e^{-|e^{\lambda}z|} e^{\lambda} dz}
						{\int_{S}{} \frac{1}{2}e^{-|z|}dz} \\
						= & \frac{e^{-|e^{\lambda}z|} e^{\lambda}}{e^{-|z|}}
						= \frac{e^{\lambda} h(e^{\lambda} z)}{h(z)}\\
	\end{split}
	\end{equation*}

	Then, we proof the property in cases of $\lambda > 0$ and $\lambda < 0$:

	\item \textbf{case 1: $\lambda > 0$}

	\begin{equation*}
	\begin{split}
	\because\ 		& 	h(e^{\lambda} z) =  \frac{1}{2} e^{-|e^{\lambda} z|} < \frac{1}{2} e^{-|z|} = h(z)\\
	\therefore\		& 	\frac{Pr[z \in e^{\lambda} S]}{Pr[z \in S]} 
					% 	= \frac
					% 	{\int_{e^{\lambda} S}{} \frac{1}{2}e^{-|z|} dz}
					% 	{\int_{S}{} \frac{1}{2}e^{-|z|} dz} 
					% 	= \frac
					% 	{\int_{S}{} \frac{1}{2}e^{-|e^{\lambda}z|} e^{\lambda} dz}
					% 	{\int_{S}{} \frac{1}{2}e^{-|z|}dz} \\
					% &	= \frac{e^{-|e^{\lambda}z|} e^{\lambda}}{e^{-|z|}}
						= \frac{e^{\lambda} h(e^{\lambda} z)}{h(z)}
						\leq e^{\lambda}\\
	\therefore\		&	ln(\frac{e^{\lambda} h(e^{\lambda} z)}{h(z)})
						\leq \lambda \\
	\because\		&	\lambda \leq \beta = \frac{\epsilon}{2 ln(3 / \delta)}, \delta < 1 \\
	\therefore\		&	\lambda \leq \frac{\epsilon}{2} \\
	\therefore\		&	\frac{Pr[z \in e^{\lambda} S]}{Pr[z \in S]} \leq \frac{\epsilon}{2} \\
	\end{split}
	\end{equation*}
